---
output:
  word_document: default
  html_document: default
---
# BAN 502 Week 1 Assignment 3
## Huffman, Abigail
### R and RStudio Refresher


```{r include=FALSE}
#install.packages("tidyverse")
library(tidyverse)
```

```{r include=FALSE}
library(ggplot2)
diamonddata = diamonds
#str(diamonddata)
```

```{r Task 3}
ggplot(diamonddata, aes(x = carat, y = price)) +
  geom_point()
```

**The scatter plot seems to indicate that as the carat size increases, the price increases as well.**  

```{r Task 4}
ggplot(diamonddata, aes(x = carat, y = price, color = cut)) +
  geom_point()
```

**In general, as the carat size increases, the price increases. Adding in the variable of cut, we can see that the quality of the cut makes an impact on price. A diamond of ideal cut will cost more at a smaller carat size than a diamond of fair cut at the same carat size**  

```{r Task 5}
ggplot(diamonddata, aes(x = carat, y = price, color = cut)) +
  geom_point() +
  facet_wrap(~ color)
```

**For each color, we see that cut and carat are important factors when considering price. A more ideal cut yields a higher price at a lower carat size. This facet of graphs shows us that color is important when determining price as well. A better color, like D, will cost you more than a lower quality color at the same carat and cut.**  

```{r Task 6 and 7}
inventory <- read_csv("InventoryData.csv")
#summary(inventory)
#str(inventory)

inventoryA <- inventory %>%
  filter(Supplier == "A")
#str(inventoryA)
```

**There are 3,695 rows in data frame inventoryA.**  
**The code in task 8 will take the inventoryA data frame and create a new variable called OnHandRatio that will be the result of taking the Annual Demand number and dividing it by the On Hand inventory number.**

```{r Task 9}
avg_cost <- inventoryA %>%
  group_by(`Item SKU`) %>%
  summarise(SKUAvgCost = mean(`Cost per Unit ($)`, na.rm = TRUE), .groups = 'drop')
```

**In previous courses, I didn't learn about things like facet_wrap or Esquisse. Those were new for me. I also had trouble with task nine and had to find how to use .groups =.Everything else was a great refresher.**